Article 2:	Information-Seeking Behavior Decision-Making between Online Search and Interpersonal Networks: The Case of Covid-19 Vaccinations 

### 2022-01-24 paper2.Rmd
Table 1 findings written

<!-- TODO this needs a lot of work but its a start -->

@@

# Discussion

summary of purpose of paper

We contribute to the literature by using a multivariable approach to identify
the sociodemographic factors associated with specific panethnic label
preferences among Latinos/Hispanics. Specifically, we focus on how U.S. region,
generation-since-immigration, racial identification, citizenship status,
language use, national origin, education, and political affiliation shape
panethnic label preference. We also call attention to factors associated with no
preference at all for these terms

table 1 and 2 main findings

- receive info from any source increases searching for information 
- older respondents more likely to search for information, perhaps indicating that 
they are less likely to trust initial sources and dig deeper, perhaps indicating less
polarization among older groups? 
- higher education more likely to seek out  more information, also seen in table 2
- blacks more likely to seek out more information
usage of different information search vehicles varies by demographics and also reception of different ifnromation
- overall, receiving information about Covid-19 vaccination generally spurs information seeking behaviors, though there are variations
- receive info from doctor leads to searching info from doctor, likely indicates good communication and trust in doctor, solid relationship with healthcare professionals
- few things predict seeking out information from another person, personal networks are so embedded in everyday life so perhaps don't remember doing it or behavioral prediction is notoriously hard
- Received Info, Social Networking Site negatively predicts Online Forum, indicating that if your social networks fulfill your need for information you don't need to extend out to online forums to ask for things, need is already met? 
- Asians are really unlikely to use online forums to find information in this context, very strong association but hispanics are more likely than non-hispanics to search online 
- online search is much less likely from those with higher education, which is counter intuitive since they are the population that has been the most trained in research methods and critical thinking .. perhaps they trust the information that they hear if they consider it to be a trusted source (typical higher education format of trust the professor) so they don't look deeper into it? basically already have high social capital in other ways, already set up to receive the information they needed and trusted
- older populations are more likely to 'just google it'

@@

# Conclusion

>>>>

<!-- TODO this needs a lot of work but its a start -->
Previous research has greatly failed to distinguish between the activation of
information seeking behaviors online and offline. In this paper, I aim to
uncover just how different various methods of information search are and begin a
line of research inquiry that investigates the factors associated with each vehicle. 
Finally, I also aimed to uncover how the different fountains of information and
information search vehicles hold real world consequences through their associations
with Covid-19 vaccination rates and intentions.

@@

# Discussion
Previous research in Sociology and Infodemiology has greatly failed to
distinguish between the activation of information seeking behaviors online and
offline. In this paper, I aim to uncover just how different various methods of
information search are and begin a line of research inquiry that investigates
the factors associated with each different vehicle. Finally, I also aimed to
uncover how the different fountains of information and information search
vehicles hold real world consequences through their associations with Covid-19
vaccination rates and intentions.

I first find that receiving information about Covid-19 vaccinations from any
outlined source increases the likelihood of searching out more information. I
also find important demographic differences in the overall propensity to seek
out information. First, I find that the older a respondent is, the more likely
they are to seek out information about Covid-19 vaccinations, possibly
indicating [???? TODO]. Furthermore, I find that those who are more educated,
that is my respondents who hold an Associate's degree or higher were more likely
to seek out information; for the most part this trend can be observed in Table
\@ref(tab:table-model-2) as well. Human Capital Theory [@mirowsky_ross98] may
help to explain this finding; this theory claims that education helps
individuals gaining health-related knowledge and use this knowledge to be
proactive in their own lives. Finally, I find that my respondents who identified
as Black were more likely to seek out further information; this may be explained
by the maltreatment that African-Americans have endured in the US
healthcare system [@baileyStructuralRacismHealth2017] which has led to major
distrust of the medical establishment among the population [@center2019a; @murray15].

(May need to cite [@bronson2014don] above or elsewhere)

table 2 main findings

usage of different information search vehicles varies by demographics and also reception of different ifnromation
- overall, receiving information about Covid-19 vaccination generally spurs information seeking behaviors, though there are variations
- receive info from doctor leads to searching info from doctor, likely indicates good communication and trust in doctor, solid relationship with healthcare professionals
- few things predict seeking out information from another person, personal networks are so embedded in everyday life so perhaps don't remember doing it or behavioral prediction is notoriously hard
- Received Info, Social Networking Site negatively predicts Online Forum, indicating that if your social networks fulfill your need for information you don't need to extend out to online forums to ask for things, need is already met? 
- Asians are really unlikely to use online forums to find information in this context, very strong association but hispanics are more likely than non-hispanics to search online 
- online search is much less likely from those with higher education, which is counter intuitive since they are the population that has been the most trained in research methods and critical thinking .. perhaps they trust the information that they hear if they consider it to be a trusted source (typical higher education format of trust the professor) so they don't look deeper into it? basically already have high social capital in other ways, already set up to receive the information they needed and trusted
- older populations are more likely to 'just google it'

@@

# Conclusion
Previous research has greatly failed to distinguish between the activation of
information seeking behaviors online and offline. In this paper, I aim to
uncover just how different various methods of information search are and begin a
line of research inquiry that investigates the factors associated with each vehicle. 
Finally, I also aimed to uncover how the different fountains of information and
information search vehicles hold real world consequences through their associations
with Covid-19 vaccination rates and intentions.
